INTELLIGENT SYSTEMS

### 2021-03-28 paper_2.tex
finish 2.4.1

>>>>

\subsection{APPLICATIONS}
\subsubsection{Class Segmentation}
An SVM-based multi-class object classifier trained on the histograms of the generated 
superpixels was used. In order for similar superpixels to have the same 
label, a conditional random field (CRF) is used to refine the segmentation. 
Thanks to this model, the prediction made by the classifier will also 
take into account the neighbors superpixels to the one to be labeled. The 
method used is that proposed in \cite{0781426534} where the main unit of measurement is 
that of the superpixel. In \cite{0781426534} the quick shift (\emph{QS}) algorithm is used for the 
generation of superpixels. The experiments were conducted on the \emph{Graz-02} 
database \cite{0781426535} containing already labeled objects. The accuracy achieved by 
the QS, ERS, SLIC and LSC algorithms is that shown in the Table \ref{table accuracy}, while 
the various segmentations, obtained from each of these, are visible in the 
figure \ref{fig: superpixelSegmentation}. As you can see, LSC performs a better segmentation than the other 
methods, this happens because the information obtained from the histograms 
belonging to the SIFT of different superpixel generated are used. In this way 
there is a better adherence to the boundary of each object in addition the 
superpixels take on a highly irregular shape for objects in the foreground and 
more regular for the background.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
        \hline
        & QS & ERS & SLIC & LSC\\
        \hline
        bike & 72.2 & 74.2 & 76.3 & \bfseries{76.9}\\
        cars & 72.2 & 74.7 & 72.5 & \bfseries{76.8}\\
        person & 66.3 & 66.5 & 66.7 & \bfseries{67.0}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Accuracy using different superpixels algorithms.}
    \label{table accuracy}
\end{table}

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
    \centering
    \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
    \label{fig: superpixelSegmentation}
\end{figure}
